---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
```

# vary
Improve readability and ease the implementation of techniques for processing 
unstructured data from varying sources. 

## Overview
A collection of methods intended to improve the resilience of a data pipeline by 
relying on pattern detection to define table dimensions, filter rows, or separate 
attributes of flattened data. For situations where connection points return data 
that has varying naming conventions, table sizes, file types, or is completely 
unstructured, and additional processing is required to ensure field consistency
prior to the use of typical data manipulation methods.

## Installation

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ulchc/vary")
```

## Usage

After installation from GitHub, you can load it with:

```{r}
library(vary)
```

## Documentation

```{r, eval=FALSE}
?vary::which_rows()
?vary::files_matching()
?vary::flatten_page_list()
# ?vary::get_downloads_folder()
# ?vary::proper_case()
?vary::clean_cols_in()
?vary::clean_cols_out()
?vary::drop_na_rows()
?vary::drop_na_cols()
# ?vary::load_required()
# ?vary::`%notin%`
```
